\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-17 evaluation.tex
update to evaluation

Modeling Fabric required approximately 5 person months. Although this is a
significant amount of time, it is a one time effort (once per release). Our plan is to reuse the developed Fabric model 
for testing arbitrary user services built for the Azure Service Fabric system.

@@

For MigratingTable, the upper section of the table uses the random input generator described in Section~\ref{sec:mtable:input}.  For each bug that led to at least one test failure, we manually reviewed one of the failure traces to confirm it reflected the intended bug.  For each of the remaining bugs, we repeated the test using a test case custom written to trigger that particular bug in order to confirm that the failure to detect the bug in the original test was due to unlucky random choices of inputs and schedules and not some other problem with the experimental setup.  These results are in the lower section of the table; they can serve as additional cases in which to compare the random and PCT schedulers but do not represent a testing method one could use to find unknown bugs in software.  It may have been interesting to report results for specific test cases written before we knew the bugs as mentioned in \ref{sec:mtable:input}, but we did not do so in this study. \PDComment{this paragraph needs to be trimmed down probably}

One of the bugs, QueryStreamedBackUpNewStream, that we found using \psharp in MigratingTable stands out because it reflects the type of oversight that tends to occur as designs evolve. Although this bug could be potentially found with other approaches, \psharp discovered it in a matter of seconds. The developers spend about 10 minutes analyzing the trace to diagnose what was happening; granted, this was after days of experience analyzing MigratingTable traces. The developers had also added their own trace output to the \psharp test harness, since \psharp's built-in trace output is too low-level and does not include event payloads and other diagnostic data that is not passed between machines.

>>>>

Modeling Fabric required approximately 5 person months. Although this is a
significant amount of time, it is a one time effort (once per release). \PDComment{should say that 5 months is required for release 1.0, subsequent releases should be much faster} Our plan is to reuse the developed Fabric model 
for testing arbitrary user services built for the Azure Service Fabric system.

@@

For the MigratingTable case study, the first 7 bugs in Table~\ref{tab:testing} were discovered using a \psharp test harness based on nondeterministically generated, but controlled by \psharp, input history. For each of these found bugs, we manually reviewed one of the bug traces to confirm if it reflected the expected bug. The remaining 4 bugs (denoted with $\diamond$) are known bugs that we were unable to find with the fully-randomized test harness in the 100,000 iterations. We believe this is due to unlucky random choices of inputs and schedules by the \psharp systematic testing engine. We wrote a custom \psharp test harness for each of these bugs, which allowed \psharp to quickly reproduce them. Note that using a custom test harness does not represent a testing method one could use to find unknown bugs in software. However, in this case the objective was to simply reproduce these known bugs.

The QueryStreamedBackUpNewStream bug in MigratingTable, that was found using \psharp, stands out because it reflects the type of oversight that tends to occur as designs evolve. We will not discuss the details of the bug due to space constraints, but \psharp managed to discover this bug in a matter of seconds. The MigratingTable developers spent about 10 minutes analyzing the trace to diagnose what was happening; granted, this was after days of experience analyzing traces. The developers had to extend the logging of \psharp with additional trace information to understand the bug. This is expected since \psharp only outputs trace information related to its communicating state machines. The trace information can be easily extended though; this was done in all our case studies.
